Summer 2025 ToDo

### 2025-11-14 Relations/Paper/Summer_2025_TODO.tex
todoo update post submission

\section*{Plan for PLDI submission}
\begin{todolist}
  \item[X] Aim for first draft finished by the end of the 29th.
  \item[\done] Make a main file at this point to conform to this conference's style. Possibly a sub-folder for each conference.
  \item [\done] discussion env has qed boxes which shouldn't be there.
  \item[\done] from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
  Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!) 
  \item [\done] Make consistent how we display definitions. 
  \item [\done] Work on the conclusion
  \item [\done] Need to fix how we put urls in for bibliography. Currently not quite working. \sacomment{Now all urls, if happy with how it looks we can tick it off. }
  \item [\done] Check the PLDI page for submission rules/requirements. In particular the bibliography style 
  \item [\done] Run through and compile everything, make sure we didn't introduce any bugs
  \item [\done] Check the layout of figures through the paper. Counterexamples for example is currently `off'.
  \item talk about why we use agda in 1.2 Agda is the perfect system for formalizing programming language theory.  
  \item Submit 
  \item Add a paragraph or two giving a short overview/summary of Agda.
  \item Go through the code, make naming consistent and self-documenting
  \item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
  \item Consider adding some more motivations 
  \item Look at the seq-minus vs. seq-not-not issue 
  \item Final read through (wed?)
  \item make an external bibliography file rather than inlining in main file. Make sure bibliography is up to standard (e.g. emph on book title).
\item Submission deadline is Thursday 13th 
\item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code). Similarly it should be the double arrow iff. Check through paper for similar changes. 
\end{todolist}

\section*{Post pldi todos}
\begin{todolist}
  \item Make the well founded definitions conform to the style of the definitions in other sections. Namely, bring the symbols to the start of the sentence. Use bemph where appropriate. Do we want all definitions to be itemized?
  \item Improve how we write P bar bar for the definitions in wellfounded (well founded minimality wise). Chat makes the following suggestion (see commented out line in tex file):
  % \newcommand{\dneg}[1]{\overline{\smash{\overline{#1}}\vphantom{#1}}} % tight double overline
  \item The sigma symbol was being rendered as a degree symbol. Why? Also, our solution is slightly too big, try and make it smaller (see well founded classical definitions).
  \item We made a bodge fix for not right arrow in use in well founded. It is good enough for now but there should be a better way to express it in latex. (when defining isMinDec)
  \item run through the table again and check the counterexamples line up.

>>>>

\section*{Plan for PLDI submission}
\begin{todolist}
  \item[X] Aim for first draft finished by the end of the 29th.
  \item[\done] Make a main file at this point to conform to this conference's style. Possibly a sub-folder for each conference.
  \item [\done] discussion env has qed boxes which shouldn't be there.
  \item[\done] from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
  Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!) 
  \item [\done] Make consistent how we display definitions. 
  \item [\done] Work on the conclusion
  \item [\done] Need to fix how we put urls in for bibliography. Currently not quite working. \sacomment{Now all urls, if happy with how it looks we can tick it off. }
  \item [\done] Check the PLDI page for submission rules/requirements. In particular the bibliography style 
  \item [\done] Run through and compile everything, make sure we didn't introduce any bugs
  \item [\done] Check the layout of figures through the paper. Counterexamples for example is currently `off'.
  \item [\done] talk about why we use agda in 1.2 Agda is the perfect system for formalizing programming language theory.  
  \item Submit 
  \item [\done] Add a paragraph or two giving a short overview/summary of Agda.
  \item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
  \item Consider adding some more motivations 
  \item Look at the seq-minus vs. seq-not-not issue 
  \item Final read through (wed?)
  \item [\done] make an external bibliography file rather than inlining in main file. Make sure bibliography is up to standard (e.g. emph on book title).
  \item Submission deadline is Thursday 13th 
\end{todolist}

\section*{Post pldi todos}
\begin{todolist}
  \item Make the well founded definitions conform to the style of the definitions in other sections. Namely, bring the symbols to the start of the sentence. Use bemph where appropriate. Do we want all definitions to be itemized?
  \item Improve how we write P bar bar for the definitions in wellfounded (well founded minimality wise). Chat makes the following suggestion (see commented out line in tex file):
  % \newcommand{\dneg}[1]{\overline{\smash{\overline{#1}}\vphantom{#1}}} % tight double overline
  \item The sigma symbol was being rendered as a degree symbol. Why? Also, our solution is slightly too big, try and make it smaller (see well founded classical definitions).
  \item We made a bodge fix for not right arrow in use in well founded. It is good enough for now but there should be a better way to express it in latex. (when defining isMinDec)
  \item Go through the code, make naming consistent and self-documenting
  \item run through the table again and check the counterexamples line up. 
  \item MF and WN iff NF (see in hierarchy section) should be an intersection rather than logical and (change to be made in paper and agda code). Similarly it should be the double arrow iff. Check through paper for similar changes.
